\sffamily An EEG-based visual Brain-Computer Interface for gaze-free communication

### 2024-10-06 chapters/wcble.tex
Resturcture chap 1 and 2
Update bttda formulation
cover page

\todo{comments liesel}
Sections~\ref{sec:wcble/literature/contrib} and~\ref{sec:wcble/methods} were published
by~\textcite{VanDenKerchove2024}

@@

\Ac{eeg}-based visual oddball \acp{bci} establish communication with paralyzed
individuals by decoding \acp{erp} obtained from time-modulated flashing
stimuli.
These \acp{erp} consist of multiple \ac{erp}-components, peaks and troughs in
\ac{erp} waveform.\todomvh{refer to image in bci chapter}
These components each have their own distinct amplitude and latency.
\Ac{erp} component latency can reflect a wide range of cognitive,
neurophysiological and clinical properties, that can be confounding factors in
the development of \acp{bci}.\todo{cite}
Latency is often assessed as the timing of an \ac{erp} component peak, obtained
after averaging over trials.
Latencies of non-averaged, single-trial \acp{erp} should capture even more
relevant information, yet they are very hard to measure due to low \ac{snr} of
single trial \acp{erp}.
Within-session variability of \ac{erp} latency, called \ac{erp} latency
\emph{jitter}, has been shown to influence \ac{bci}
accuracy~\cite{Thompson2012}.
This effect is especially prominent when bringing \ac{bci} development from the
lab to the clinical setting with patients in the target population.
\textcite{Zisk2021} showed that patients with \ac{als} have significantly
increased ERP jitter.
\textcite{Arico2014} show that latency jitter negatively affects \ac{bci}
performance, and disproportionally so when the user is not directly gazing at
intended targets, such as is the case for gaze-impaired patients.

\subsection{\Acs{erp} latency jitter}

\subsubsection{Neural origins of latency jitter}
While the classic \ac{erp} model assumes a constant \ac{erp} response over trials,
research has shown that cortical evoked potentials show significant
trial-to-trial jitter~\cite{Truccolo2002}.
Experiments show that latency jitter in \acp{erp} is the result of the interaction of
the evoked activity with ongoing dynamics in the brain~\cite{Hasenstaub2007,
	Kisley1999, Curto2009, Arieli1996}.
According to the Firefly model of event-related activity~\cite{Burgess2012},
the latency of an evoked potential results from a combination of the modulation
of oscillating activity that is time-locked, but not necessarily phase-locked to stimulus onset,
and a delay caused by ongoing neurophysiological processes that are not necessarily related to the task
\cite{Stokes2016,Mouraux2008}.
\todo{substantiate}

\subsubsection{Implications for \ac{erp} analysis}

The presence of latency jitter introduces multiple issues to \ac{erp} analysis, the
most prominent of which is the smearing effect as illustrated
in~\autoref{fig:wcble/smearing}. In \ac{erp} analysis, single-trial \acp{erp} are usually
averaged per condition to cope with the unfavorable \ac{snr}?
When averaging over multiple identical responses with jittered latencies, the shape
and amplitude of the average do not reflect the properties
of the original signal.
Because the amplitude of the average is lower, the \ac{snr} will also be negatively impacted.
More generally, the smearing effect leads to difficulties interpreting \ac{erp}
results and making inferences about amplitude or latency effects, because these
are entangled when using averaging~\cite{Woody1967, Pfefferbaum1980, McDowell2003, Verleger2005,
	Roth2007, Walhovd2008, Poli2010, Luck2014}\todo{Review relevance of
	these references}.

\begin{figure}[t]
  \centering
  \input{figures/wcble/smearing.tikz.tex}
  \caption[The smearing effect.]{The smearing effect. When obtaining an \ac{erp} template through
  averaging, high jitter causes a decrease in peak amplitude and a deformation
  of the shape of the waveform.}
  \label{fig:wcble/smearing}
\end{figure}

\todo{illustrate smearing effect}

@@

\subsubsection{Benefits of latency estimation}
A common approach to counteract the smearing effect is to correct single-trial
\acp{erp} for jitter before averaging.\todo{reference}
This can be done by estimating the latency of each
single-trial \ac{erp}, and aligning them before averaging.
Latency estimation has multiple advantages:
\begin{enumerate*}[label={(\arabic*)}]
	\item Latency-based \ac{erp} alignment can help reveal the true shape and
	properties like peak amplitude and latency of \acp{erp} across
	experimental conditions. These are variables of interest for
	testing electrophysiological an behavioral hypotheses.
	Additionally, latency estimation allows for the extraction of
	other descriptors from a set of single-trial \acp{erp}, like
	amplidute or latency variance~\cite{Hultsch2004}, which can
	also be of interest as studied variables.
  For instance, in the work of \textcite{Saville2014}, the inter-trial latency
  variability itself is determined as a correlate of working memory performance.
	\item Counteracting the smearing effect will boost the signal-to-noise
	ratio of averaged \acp{erp} by increasing the amplitude of the
	\ac{erp} signal. This in turn can reveal smaller or more jittered \ac{erp}
  components which would otherwise obscured or blurred due to desynchronization.
    These \emph{deblurred} templates can then be used for analysis of the \ac{erp}
	waveform, or as templates of the signal of interest in
	\acp{bci}~\cite{Arico2014}.
	%this enables decoders to take into account the relatively low amplitude
	%earlier components, leading to applications in settings where
	%information from other components than the P300 need to be exploited,
	%like covert visual attention paradigms~\cite{arico2014influence,
	%hardiansyah2020single}.\todo[inline]{rework this to latency features
	%because smaller visual components might not really be revealed
	%since they're already time-locked}
	\item Finally, the introduction of latency estimation and alignment generally
	improves \ac{bci} classification performance.
  Single-trial latencies can be	used as features to improve
  classification~\cite{Hardiansyah2020}.
	Furthermore, compensating for inter-trial differences, especially when
	extended to inter-session or inter-subject differences, can aid in transfer learning or
	generalization across subjects and protocols\cite{Iturrate2014}.
\end{enumerate*}

@@

Template matching is generally preferred to peak picking.
The algorithm proposed by \textcite{Woody1967} in 1976 is a simple and elegant
latency estimation method that is still being used and is even
considered amongst the more performant techniques for \acp{erp}~\cite{Ouyang2017}.
It starts with an average \ac{erp} as a rough estimation of the aligned template
\ac{erp}, and iteratively refines this template by determining at each step the time point of maximum
cross-correlation of this template with all single-trial \acp{erp} and aligning them
on these time points to form the next template.
Similarily, cross-correlation template matching can be combined with filtering.
\cite{Souloumiac2013} uses XDAWN to construct spatial filter before
template matching the spatially filtered signal. \cite{Iturrate2014} uses a
spatiotemporal filter. Instead of aligning the
latencies to obtain the template for the next iteration, weighted averaging can
also be used~\cite{Gasser1983}.
\todo{cite Thornton2008 hierarchical woody?}

@@

\todo{cite Kim2020 used to analyze the difference between target and
non-target}

@@

\subsection{Robust \ac{cble} latency features}
\label{sec:robust-latency}
The \ac{erp} decoding method based on \ac{cble} introduced by \cite{Mowla2017} does
not make use of the extracted latencies, only passing score matrix $\mat{Y}$ on
to the second-stage classifier.
Furthermore, previous \ac{cble} works~\cite{Thompson2012,Mowla2020} only used these
latencies to correlate them with neurophysiological processes or to predict
decoder performance.
We noticed that, while \ac{cble} performance was unaffected, the classification
performance of our proposed method can be improved if the estimated
latencies are also made available as features to the second-stage classifier,
after a square transform for linear separability~\cite{Thompson2012}.

@@

}{%
  Schematic representation of the \ac{wcble} test phase.
}{%
  Schematic representation of the Woody Classifier Based Latency
  Estimation test phase. (1) The
	first-stage	spatiotemporal binary classifier obtained from the training phase is
	applied to time-shifted copies of the epochs to obtain scores and class probabilities
	over time. (2) The medians of these probability distributions are assumed
	as the new class latencies. (3) The scores and class latencies are input to the
  trained second-stage classifier, which predicts the label of the epochs.
}{%
  fig:diagram-eval
}
\todo{Pr not italic}
\todo{re-insert comments}

\begin{algorithm}[H]
	\textsc{Train}
	\smallskip \hrule \smallskip
	\textbf{Input:} $\{\mat{X}_n^\mathrm{train}\}_{n=1}^N,
  \mathbf{l}^\mathrm{train}, \mathcal{C}(\cdot,f, \Pr), s_1, s_2$
  \begin{algorithmic}[1]
		\State $\theta \gets
			\mathrm{train}_\mathcal{C}(\{\mat{X}_n^\mathrm{train}[:,s_1:s_2]\}_{n=1}^N,\mathbf{l})$
      %\algorithmiccomment{Train stage 1}
		\For{$n=1\ldots N$}
      %\algorithmiccomment{Feature extraction for stage 2}
		  \For{$s=1\ldots R$}
      \State $y_{n,s}^\mathrm{train} \gets f(\mat{X}_n^\mathrm{train}[:,s:s+(s_2-s_1)],\theta)$
        \EndFor
        \State $s_{n,\mathrm{target}}^\mathrm{train} \gets
			    \mathrm{median}\left[Pr(s|\mat{X}_n^\mathrm{train},\theta,\mathrm{target})\right]$
		    \State $s_{n,\mathrm{non-target}}^\mathrm{train}\gets
			    \mathrm{median}\left[Pr(s|\mat{X}_n^\mathrm{train},\theta,\textrm{non-target})\right]$
    \EndFor
	\end{algorithmic}
  \textbf{Output:} $\theta,
  \mat{Y}^\mathrm{train},
  \mathbf{s}_\mathrm{target}^\mathrm{train},
  \mathbf{s}_\mathrm{non-target}^\mathrm{train}$
	\smallskip \hrule \smallskip
	\textsc{Evaluate}
	\smallskip \hrule \smallskip
	\textbf{Input:} $\{\mat{X}_m^\mathrm{test}\}_{m=1}^N, \mathcal{C}(\theta,f, \Pr), s_1, s_2$
  \begin{algorithmic}[1]
		\For{$m=1\ldots M$}
      %\algorithmiccomment{Feature extraction for stage 2}
		  \For{$s=1\ldots R$}
      \State $y_{m,s}^\mathrm{test} \gets f(\mat{X}_n^\mathrm{test}[:,s:s+(s_2-s_1)],\theta)$
        \EndFor
        \State $s_{m,\mathrm{target}}^\mathrm{test} \gets
			    \mathrm{median}\left[Pr(s|\mat{X}_m^\mathrm{test},\theta,\mathrm{target})\right]$
		    \State $s_{m,\mathrm{non-target}}^\mathrm{test}\gets
			    \mathrm{median}\left[Pr(s|\mat{X}_m^\mathrm{test},\theta,\textrm{non-target})\right]$
    \EndFor
	\end{algorithmic}
  \textbf{Output:} $\mat{Y}^\mathrm{test},
  \mathbf{s}_\mathrm{target}^\mathrm{test},
  \mathbf{s}_\mathrm{non-target}^\mathrm{test}$

@@

\begin{algorithm}[H]
	\textsc{Train}
	\smallskip \hrule \smallskip
	\textbf{Input:} $\{\mat{X}_n^\mathrm{train}\}_{n=1}^N, \mathbf{l})
		\mathcal{C}(\cdot,f,\Pr), s_1, s_2$
	\begin{algorithmic}[1]
		\State $\mat{X}'_n \gets \mat{X}^\mathrm{train}_n \quad \forall \quad n=1\ldots
    N$
      %\algorithmiccomment{Train stage 1}
		\Repeat
		\State $\theta^* \gets \mathrm{train}_\mathcal{C}(\{\mat{X}'_n[:,s_1:s_2]\}_0^{N-1},\mathbf{l}$
		\For{$n=1\ldots N$}
    \State  $s_n \gets
			    \mathrm{median}\left[Pr(s|\mat{X}_n',\theta^*,l_n)\right]$
		\State $\mat{X}'_n \gets \mathrm{align}(\mat{X}^\mathrm{train}_n, s^*_n)$
		\EndFor
    \Until{convergence or maximum iterations reached}
    \For{$n=1\ldots N$}%\algorithmiccomment{Feature extraction for stage 2}
		  \For{$s=1\ldots R$}
      \State $y_{n,s}^\mathrm{train} \gets
      f(\mat{X}_n^\mathrm{train}[:,s:s+(s_2-s_1)],\theta^*)$
        \EndFor
        \State $s_{n,\mathrm{target}}^\mathrm{train} \gets
			    \mathrm{median}\left[Pr(s|\mat{X}_n^\mathrm{train},\theta^*,\mathrm{target})\right]$
		    \State $s_{n,\mathrm{non-target}}^\mathrm{train}\gets
			    \mathrm{median}\left[Pr(s|\mat{X}_n^\mathrm{train},\theta^*,\textrm{non-target})\right]$
    \EndFor

@@

	\smallskip \hrule \smallskip
	\textsc{Evaluate}
	\smallskip \hrule \smallskip
	\textbf{Input:} $\{\mat{X}_m^\mathrm{test}\}_{m=1}^N, \mathcal{C}(\theta^*,f, \Pr), s_1, s_2$
  \begin{algorithmic}[1]
		\For{$m=1\ldots M$}%\algorithmiccomment{Feature extraction for stage 2}
		  \For{$s=1\ldots R$}
      \State $y_{m,s}^\mathrm{test} \gets
      f(\mat{X}_n^\mathrm{test}[:,s:s+(s_2-s_1)],\theta^*)$
        \EndFor
        \State $s_{m,\mathrm{target}}^\mathrm{test} \gets
			    \mathrm{median}\left[Pr(s|\mat{X}_m^\mathrm{test},\theta^*,\mathrm{target})\right]$
		    \State $s_{m,\mathrm{non-target}}^\mathrm{test}\gets
			    \mathrm{median}\left[Pr(s|\mat{X}_m^\mathrm{test},\theta^*,\textrm{non-target})\right]$
    \EndFor
	\end{algorithmic}
  \textbf{Output:} $\mat{Y}^\mathrm{test},
  \mathbf{s}_\mathrm{target}^\mathrm{test},
  \mathbf{s}_\mathrm{non-target}^\mathrm{test}$
  \caption{\ac{wcble}}
	\label{alg:wcble}
\end{algorithm}

@@

\begin{figure}[!ht]
  \input{figures/wcble/fig_latency.pgf} \\
  \input{figures/wcble/fig_accuracy.pgf}
  \caption{caption}
  \label{fig:wcble/results/latency}
\end{figure}
\todo{properly label axes}
\todo{uniform fonts with rest of document}
\todo{correct width}
\todo{figure for data generation}

@@

\subsection{Classification}
\todo{refer to figure}
Analogous to the previous experiment, 10-fold cross-validated classification
accuracy between target and non-target epochs was assessed.
Here, \ac{wcble} was compared to \ac{cble}, but both also to their base classifier
\ac{tlda}.
\Ac{cble} and \ac{wcble} classifiers were implemented as described
in~\ref{sec:wcble/methods}, with both the wavelet transformed score time series
and square transformed latencies as input to a second-stage logistic regression
classifier with $L_2$-norm regularization ($C=0.2$).
\todo{ref figure}

>>>>

\label{sec:wcble}
\todo{comments liesel}
\emph{Sections~\ref{sec:wcble/literature/contrib} and~\ref{sec:wcble/methods} were published
as part of~\textcite{VanDenKerchove2024}}

@@

\Ac{eeg}-based visual oddball \acp{bci} establish communication with paralyzed
individuals by decoding \acp{erp} obtained from time-modulated flashing
stimuli (see Figure~\ref{fig:bci/loop}).
These \acp{erp} consist of multiple \ac{erp}-components, peaks and troughs in
\ac{erp} waveform (see Figure~\ref{fig:bci/erp}.
These components each have their own distinct amplitude and latency.
\Ac{erp} component latency can reflect a wide range of cognitive,
neurophysiological and clinical properties, that can be confounding factors in
the development of \acp{bci}~\cite{Luck2014}.
Latency is often assessed as the timing of an \ac{erp} component peak, obtained
after averaging over trials.
Latencies of non-averaged, single-trial \acp{erp} should capture even more
relevant information, yet they are very hard to measure due to low \ac{snr} of
single trial \acp{erp}.
Within-session variability of \ac{erp} latency, called \ac{erp} latency
\emph{jitter}, has been shown to influence \ac{bci}
accuracy~\cite{Thompson2012}.
This effect is especially prominent when bringing \ac{bci} development from the
lab to the clinical setting with patients in the target population.
\textcite{Zisk2021} showed that patients with \ac{als} have significantly
increased ERP jitter.
\textcite{Arico2014} show that latency jitter negatively affects \ac{bci}
performance, and disproportionally so when the user is not directly gazing at
intended targets, such as is the case for individuals with \ac{sspgi}.
Therefore, properly accounting for \ac{erp} latency jitter can contribute to
the development of gaze-independent visual \acp{bci}.

\subsection{Neural origins of \ac{erp} latency jitter}
While the classic \ac{erp} model assumes a constant \ac{erp} response over trials,
research has shown that cortical evoked potentials show significant
trial-to-trial jitter~\cite{Truccolo2002}.
Experiments show that latency jitter in \acp{erp} is the result of the interaction of
the evoked activity with ongoing dynamics in the brain~\cite{Hasenstaub2007,
	Kisley1999, Curto2009, Arieli1996}.
According to the Firefly model of event-related activity~\cite{Burgess2012},
the latency of an evoked potential results from a combination of the modulation
of oscillating activity that is time-locked, but not necessarily phase-locked to stimulus onset,
and a delay caused by ongoing neurophysiological processes that are not necessarily related to the task
\cite{Stokes2016,Mouraux2008}.
If these processes are related to the \ac{bci} task at hand, such as attention
and visual processing, jitter could have a significant impact on \ac{erp}
decoding.

\subsection{Implications for \ac{erp} analysis}

The presence of latency jitter introduces multiple issues to \ac{erp} analysis, the
most prominent of which is the smearing effect as illustrated
in~\autoref{fig:wcble/smearing}. In \ac{erp} analysis, single-trial \acp{erp} are usually
averaged per condition to cope with the unfavorable \ac{snr}?
When averaging over multiple identical responses with jittered latencies, the shape
and amplitude of the average do not reflect the properties
of the original signal.
Because the amplitude of the average is lower, the \ac{snr} will also be negatively impacted.
More generally, the smearing effect leads to difficulties interpreting \ac{erp}
results and making inferences about amplitude or latency effects, because these
are entangled when using averaging~\cite{Luck2014}.

\begin{figure}
  \centering
  \input{figures/wcble/smearing.tikz.tex}
  \caption[The smearing effect.]{The smearing effect. When obtaining an \ac{erp} template through
  averaging, high jitter causes a decrease in peak amplitude and a deformation
  of the shape of the waveform.}
  \label{fig:wcble/smearing}
\end{figure}

@@

\subsection{Benefits of latency estimation}
As we will see later, a common approach to counteract the smearing effect is to correct single-trial
\acp{erp} for jitter before averaging.
This can be done by estimating the latency of each
single-trial \ac{erp}, and aligning them before averaging.
Latency estimation has multiple advantages:
\begin{enumerate*}[label={(\arabic*)}]
	\item Latency-based \ac{erp} alignment can help reveal the true shape and
	properties like peak amplitude and latency of \acp{erp} across
	experimental conditions. These are variables of interest for
	testing electrophysiological an behavioral hypotheses.
	Additionally, latency estimation allows for the extraction of
	other descriptors from a set of single-trial \acp{erp}, like
	amplidute or latency variance~\cite{Hultsch2004}, which can
	also be of interest as studied variables.
  For instance, in the work of \textcite{Saville2014}, the inter-trial latency
  variability itself is determined as a correlate of working memory performance.
	\item Counteracting the smearing effect will boost the signal-to-noise
	ratio of averaged \acp{erp} by increasing the amplitude of the
	\ac{erp} signal. This in turn can reveal smaller or more jittered \ac{erp}
  components which would otherwise obscured or blurred due to desynchronization.
    These \emph{deblurred} templates can then be used for analysis of the \ac{erp}
	waveform, or as templates of the signal of interest in
	\acp{bci}~\cite{Arico2014}.
	%this enables decoders to take into account the relatively low amplitude
	%earlier components, leading to applications in settings where
	%information from other components than the P300 need to be exploited,
	%like covert visual attention paradigms~\cite{arico2014influence,
	%hardiansyah2020single}.\todo[inline]{rework this to latency features
	%because smaller visual components might not really be revealed
	%since they're already time-locked}
	\item Finally, the introduction of latency estimation and alignment generally
	improves \ac{bci} classification performance.
  Single-trial latencies can be	used as features to improve
  classification~\cite{Hardiansyah2020}.
	Furthermore, compensating for inter-trial differences, especially when
	extended to inter-session or inter-subject differences, can aid in transfer learning or
	generalization across subjects and protocols\cite{Iturrate2014}.
\end{enumerate*}

@@

Template matching is generally preferred to peak picking.
The algorithm proposed by \textcite{Woody1967} in 1976 is a simple and elegant
latency estimation method that is still being used and is even
considered amongst the more performant techniques for
\acp{erp}~\cite{Thornton2008, Ouyang2017}.
It starts with an average \ac{erp} as a rough estimation of the aligned template
\ac{erp}, and iteratively refines this template by determining at each step the time point of maximum
cross-correlation of this template with all single-trial \acp{erp} and aligning them
on these time points to form the next template.
Similarily, cross-correlation template matching can be combined with filtering.
\cite{Souloumiac2013} uses XDAWN to construct spatial filter before
template matching the spatially filtered signal. \cite{Iturrate2014} uses a
spatiotemporal filter. Instead of aligning the
latencies to obtain the template for the next iteration, weighted averaging can
also be used~\cite{Gasser1983}.

@@

@@

\subsection{Robust latency features}
\label{sec:robust-latency}
The \ac{erp} decoding method based on \ac{cble} introduced by \cite{Mowla2017} does
not make use of the extracted latencies, only passing score matrix $\mat{Y}$ on
to the second-stage classifier.
Furthermore, previous \ac{cble} works~\cite{Thompson2012,Mowla2020} only used these
latencies to correlate them with neurophysiological processes or to predict
decoder performance.
We noticed that, while \ac{cble} performance was unaffected, the classification
performance of our proposed method can be improved if the estimated
latencies are also made available as features to the second-stage classifier,
after a square transform for linear separability~\cite{Thompson2012}.

@@

}{%
  Schematic representation of the \ac{wcble} test phase.
}{%
  Schematic representation of the Woody Classifier Based Latency
  Estimation test phase. (1) The
	first-stage	spatiotemporal binary classifier obtained from the training phase is
	applied to time-shifted copies of the epochs to obtain scores and class probabilities
	over time. (2) The medians of these probability distributions are assumed
	as the new class latencies. (3) The scores and class latencies are input to the
  trained second-stage classifier, which predicts the label of the epochs.
}{%
  fig:diagram-eval
}
\todo{re-insert comments}

\begin{algorithm}[H]
	\textsc{Train}
	\smallskip \hrule \smallskip
	\textbf{Input:} $\{\mat{X}_n^\mathrm{train}\}_{n=1}^N,
  \mathbf{l}^\mathrm{train}, \mathcal{C}(\cdot,f, \Pr), s_1, s_2$
  \begin{algorithmic}[1]
		\State $\theta \gets
			\mathrm{train}_\mathcal{C}(\{\mat{X}_n^\mathrm{train}[:,s_1:s_2]\}_{n=1}^N,\mathbf{l})$
      %\algorithmiccomment{Train stage 1}
		\For{$n=1\ldots N$}
      %\algorithmiccomment{Feature extraction for stage 2}
		  \For{$s=1\ldots R$}
      \State $y_{n,s}^\mathrm{train} \gets f(\mat{X}_n^\mathrm{train}[:,s:s+(s_2-s_1)],\theta)$
        \EndFor
        \State $s_{n,\mathrm{target}}^\mathrm{train} \gets
			    \mathrm{median}\left[\Pr(s|\mat{X}_n^\mathrm{train},\theta,\mathrm{target})\right]$
		    \State $s_{n,\mathrm{non-target}}^\mathrm{train}\gets
			    \mathrm{median}\left[\Pr(s|\mat{X}_n^\mathrm{train},\theta,\textrm{non-target})\right]$
    \EndFor
	\end{algorithmic}
  \textbf{Output:} $\theta,
  \mat{Y}^\mathrm{train},
  \mathbf{s}_\mathrm{target}^\mathrm{train},
  \mathbf{s}_\mathrm{non-target}^\mathrm{train}$
	\smallskip \hrule \smallskip
	\textsc{Evaluate}
	\smallskip \hrule \smallskip
	\textbf{Input:} $\{\mat{X}_m^\mathrm{test}\}_{m=1}^N, \mathcal{C}(\theta,f, \Pr), s_1, s_2$
  \begin{algorithmic}[1]
		\For{$m=1\ldots M$}
      %\algorithmiccomment{Feature extraction for stage 2}
		  \For{$s=1\ldots R$}
      \State $y_{m,s}^\mathrm{test} \gets f(\mat{X}_n^\mathrm{test}[:,s:s+(s_2-s_1)],\theta)$
        \EndFor
        \State $s_{m,\mathrm{target}}^\mathrm{test} \gets
			    \mathrm{median}\left[\Pr(s|\mat{X}_m^\mathrm{test},\theta,\mathrm{target})\right]$
		    \State $s_{m,\mathrm{non-target}}^\mathrm{test}\gets
			    \mathrm{median}\left[\Pr(s|\mat{X}_m^\mathrm{test},\theta,\textrm{non-target})\right]$
    \EndFor
	\end{algorithmic}
  \textbf{Output:} $\mat{Y}^\mathrm{test},
  \mathbf{s}_\mathrm{target}^\mathrm{test},
  \mathbf{s}_\mathrm{non-target}^\mathrm{test}$

@@

\begin{algorithm}[H]
	\textsc{Train}
	\smallskip \hrule \smallskip
	\textbf{Input:} $\{\mat{X}_n^\mathrm{train}\}_{n=1}^N, \mathbf{l})
		\mathcal{C}(\cdot,f,\Pr), s_1, s_2$
	\begin{algorithmic}[1]
		\State $\mat{X}'_n \gets \mat{X}^\mathrm{train}_n \quad \forall \quad n=1\ldots
    N$
      %\algorithmiccomment{Train stage 1}
		\Repeat
		\State $\theta^* \gets \mathrm{train}_\mathcal{C}(\{\mat{X}'_n[:,s_1:s_2]\}_0^{N-1},\mathbf{l}$
		\For{$n=1\ldots N$}
    \State  $s_n \gets
			    \mathrm{median}\left[\Pr(s|\mat{X}_n',\theta^*,l_n)\right]$
		\State $\mat{X}'_n \gets \mathrm{align}(\mat{X}^\mathrm{train}_n, s^*_n)$
		\EndFor
    \Until{convergence or maximum iterations reached}
    \For{$n=1\ldots N$}%\algorithmiccomment{Feature extraction for stage 2}
		  \For{$s=1\ldots R$}
      \State $y_{n,s}^\mathrm{train} \gets
      f(\mat{X}_n^\mathrm{train}[:,s:s+(s_2-s_1)],\theta^*)$
        \EndFor
        \State $s_{n,\mathrm{target}}^\mathrm{train} \gets
			    \mathrm{median}\left[\Pr(s|\mat{X}_n^\mathrm{train},\theta^*,\mathrm{target})\right]$
		    \State $s_{n,\mathrm{non-target}}^\mathrm{train}\gets
			    \mathrm{median}\left[\Pr(s|\mat{X}_n^\mathrm{train},\theta^*,\textrm{non-target})\right]$
    \EndFor

@@

	\smallskip \hrule \smallskip
	\textsc{Evaluate}
	\smallskip \hrule \smallskip
	\textbf{Input:} $\{\mat{X}_m^\mathrm{test}\}_{m=1}^N, \mathcal{C}(\theta^*,f, \Pr), s_1, s_2$
  \begin{algorithmic}[1]
		\For{$m=1\ldots M$}%\algorithmiccomment{Feature extraction for stage 2}
		  \For{$s=1\ldots R$}
      \State $y_{m,s}^\mathrm{test} \gets
      f(\mat{X}_n^\mathrm{test}[:,s:s+(s_2-s_1)],\theta^*)$
        \EndFor
        \State $s_{m,\mathrm{target}}^\mathrm{test} \gets
			    \mathrm{median}\left[\Pr(s|\mat{X}_m^\mathrm{test},\theta^*,\mathrm{target})\right]$
		    \State $s_{m,\mathrm{non-target}}^\mathrm{test}\gets
			    \mathrm{median}\left[\Pr(s|\mat{X}_m^\mathrm{test},\theta^*,\textrm{non-target})\right]$
    \EndFor
	\end{algorithmic}
  \textbf{Output:} $\mat{Y}^\mathrm{test},
  \mathbf{s}_\mathrm{target}^\mathrm{test},
  \mathbf{s}_\mathrm{non-target}^\mathrm{test}$
  \caption{\ac{wcble}}
	\label{alg:wcble}
\end{algorithm}

@@

\begin{figure}[H]
  \input{figures/wcble/fig_accuracy.pgf}
  \caption{caption}
  \label{fig:wcble/results/latency}
\end{figure}

\todo{properly label axes}
\todo{uniform fonts with rest of document}
\todo{correct width}
\todo{figure for data generation}

@@

\subsection{Classification}

Analogous to the previous experiment, 10-fold cross-validated classification
accuracy between target and non-target epochs was assessed.
Here, \ac{wcble} was compared to \ac{cble}, but both also to their base classifier
\ac{tlda}.
\Ac{cble} and \ac{wcble} classifiers were implemented as described
in~\ref{sec:wcble/methods}, with both the wavelet transformed score time series
and square transformed latencies as input to a second-stage logistic regression
classifier with $L_2$-norm regularization ($C=0.2$).
\todo{ref figure}

\begin{figure}
  \input{figures/wcble/fig_accuracy.pgf}
  \caption{caption}
  \label{fig:wcble/results/accuracy}
\end{figure}
